rotation_runs2019

### 2020-01-06 inst/documents/rotation_runs2019.Rmd
gens under thresh now working after correction to mort_thresh and freq_thresh

nscenarios <- 20
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
id_expt <- 'D4'

>>>>

nscenarios <- 200
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

### 2020-01-06 inst/documents/rotations_notes.Rmd
gens under thresh now working after correction to mort_thresh and freq_thresh

@@

# in rotation_runs2019.Rmd uncomment the line below and re-add calc gens-under-thresh
# gens <- gens_under_thresh(dfres=dfres, threshold=threshold, mort_or_freq=linputs$mort_or_freq)

*check on new outputs : tot-gens, mean-mort

>>>>

problem that gens_u_rot and gens_u_seq both currently 0

seems to be because linputs$freq_thresh & mort thresh are both NULL

@@

#check : gens_u_rot_minus_seq

currently 0 for all 200 runs of b2
